%-------------------------
% Resume in Latex
% Author : Pawan Kumar
% License : MIT
%------------------------

\documentclass[letterpaper,10.8pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Pawan Kumar}} & Email : \href{mailto:pawanwrites93@gmail.com}{pawanwrites93@gmail.com}\\
  \href{https://www.linkedin.com/in/itspawanhere/}{Linkedin: https://www.linkedin.com/in/itspawanhere/} & Mobile : +91-911-015-5652 \\
  \href{https://github.com/itspawanhere}{Github: https://github.com/itspawanhere} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Technology, Kanpur}{Kanpur, India}
      {Masters in Computer Science;  GPA: 8.33/10}{July 2016 - May 2018}
      
	   %{\scriptsize \textit{Courses: Operating Systems, Analysis Of Algorithms, Artificial Intelligence, Machine Learning, Probability and Statistics and Network Security.}}
	    
    \resumeSubheading
      {Indian Institute of Technology, Guwahati}{Guwahati, India}
      {B.tech in Computer Science and Engineering;  GPA: 7.80/10}{July 2010 - May 2014}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{Java, C, C\texttt{++}, Javascript, Python, SQL, Unix scripting}
	\resumeSubItem{Tools}{Git, JIRA, ElasticSearch, Latex}
	\resumeSubItem{Frameworks}{Android, Scrum, Flask, ReactJS, MongoDB, Hadoop, Hive, Spark, Spring Boot, Hibernate}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Eureka Analytics}{Bangalore, IN}
    {Software Engineer}{June 2018 -  Current}
    \resumeItemListStart
        \resumeItem{Data Pipeline for Telco Dataset}
          {Built tool named ``pipecore" which can automate transformation of data from Telco file system to Eureka data format upon which AI engines can run. Built another complementary tool called ``sms-scheduler" which enabled creation of whitelist users and scheduled sending sms to end-users for various campaigns. \\ Tools/Technology Used: \textsc{Java, Hadoop, Oozie, Hive}.}
          \resumeItem{Eureka User Profile Store}
          {Built the User Interface for exploring the Telco Users and target a specific section of users based on various filters. Developed various data visualizations charts based on the dynamic filters selected. \\ Tools/Technology Used: \textsc{ReactJS, ElasticSearch, Chart-JS}.}
          \resumeItem{ApiDoc}{Modified the open-source tool called ``ApiDoc" to document entire Eureka code-base. It enabled viewing all the public/private APIs in a single place. Tools/Technology Used: \textsc{Javascript}.}
      \resumeItemListEnd
      
    \resumeSubheading
		{Samsung Research Institute}{Bangalore, IN}
		{Software Engineer}{June 2014 -  July 2016}
		\resumeItemListStart
        \resumeItem{Splitbilling}
          {Devised separate billing system with which system admin can monitor call/sms/data usage for personal and enterprise usage separately through a dashboard. \\ Tools/Technology used: \textsc{Python, MongoDB, Flask, JavaScript, Bootstrap}.}
        \resumeItem{Email Glue}
          {Worked on automation of tasks/events creation based on email content and hence enabling zero-inbox policy for Samsung email app. Additionally, developed Google Drive add-on for Samsung Email using which mail attachments can be directly integrated with Google drive. \\ Tools/Technology Used: \textsc{Android, Java, Drive SDK}.}
		\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Academic Projects}
\resumeSubHeadingListStart
\resumeSubItem{Knowledge Management System}{Developed a fully voice-automated web-application based on Watson APIs which can be trained and queried later. Optionally, the user can provide feedback to the system, which can be used to enhance the results. Technology/Tools Used: \textsc{Python, Watson SDK, Flask}. (Mar '18)}
\resumeSubItem{Breaking Ciphers - Cryptology}{}
\begin{description}[font=$\bullet$]
    \item {Broke 6-round of DES (Data Encryption Standard) by using chosen-plain text attack. Tool Used: C\texttt{++}. (Feb '17)}
    \item {Broke a special case of RSA (where public key is small) for 1024-digit long prime factors. Tool Used: \textsc{SAGE}. (Mar '17)}
    \end{description}
\resumeSubItem{Information Retrieval System}{Developed a text based retrieval system(Mini Search System) for CACM dataset. Preprocessing and Indexing the documents using Trie Tree and TF-IDF as relevance score. Technology/Tools Used: \textsc{Python, JavaScript}. (Sep '13)}
\resumeSubHeadingListEnd

%-----------Awards-----------------
\section{Honors and Awards}
\begin{description}[font=$\bullet$]
\item {Awarded Merit-cum-means Scholarship at IIT Guwahati for 4 straight years. (2010-14)} 
\item {Listed among the top 0.18 \% among 500k\texttt{+} students appearing at JEE. (May '10)}
\item {Awarded Certificate of Merit by CBSE for being among top 0.1\% of students in Social Science. (May '08)}
\item {Got first prize in state level essay competition. (May '07)}
\end{description}
%-------------------------------------------
\end{document}